\chapter{Introduction}
\label{introduction}

\section{Problem Statement}
Languages are different. Linguistic typology studies classification of world languages depending their structural and functional features. Because of the diversity of different languages, there are many criterion defined to classify languages into different groups \citep{wals}. For example, according to subject-verb-object positioning, languages can be grouped into different sets: SOV (such as French, German, Spanish and Chinese), SVO (such as English and Chinese) and so on, where the abbreviation represents the order of subject(S), verb(V) and object(O). Phonologically, patterns in the structure and distributions of sound systems are investigated to classify world's languages based on phonological properties. As summarized by \citep{wals}, properties including vowel and consonant inventory, consonant-vowel ratio, syllable structure, rhythm types, etc. are used to represent the difference in phonology across different languages. Some of those properties mainly measure segmental information while others measure supra-segmental information of one language's phonological system. Those various phonological properties result in diverse acoustic characteristics when we listen to speech recordings in different languages. Another important outcome of the those different phonological properties across languages is that when a speaker speaks in a language other than his mother tongue the speech he will be perceived to have accent, which comes from the interplay of the phonological difference of the first language (L1, the speaker's mother tongue) and second language(L2, the language the speaker is speaking). Accented speech is the focus of the study in this dissertation.

Accented speech is the result of L2 speech being produced by a sensorimotor control system that has overlearned L1 phonological patterns, including both phoneme sound contrasts and rhythmic composition. According to L1 acquisition theory, the malleability of human brain in terms of language is strongest only for a limited time (sometime between age 5 and puberty), which is referred as the critical period hypothesis. After that period, language acquisition is much more difficult. The critical period hypothesis from L1 acquisition was extended to include L2 acquisition, positing that a critical age or period after which L2 speech production could not be native like \citep{long1990maturational}. However, further research revealed that the speech learning model (SLM) accounted for exceptions that can not be explained by the critical period hypothesis. For example, it was reported that both early L2 learners failed to achieve native-like production while late L2 learners did \citep{flege1995second}. The SLM also hypothesized a shared phonological space for speech sounds and used ``equivalence classification'' to explain why a learner might not create a new phonetic category for an L2 sound perceived as similar to an L1 sound. In addition, findings in neuroscience favored the concept of a ``sensitive'' or ``optimal'' period over a ``critical'' one.

Accentedness is usually used to measure the perceived difference between accented speech produced by L2 learners and speech produced by native speakers. There are multiple ways to define accentedness. A more general definition in literature was proposed in \citep{mccullough2013acoustic} considering previous definitions: accentedness refers to perception of deviations from a pronunciation norm that a listener attributes to the talker not speaking the target language natively. This definition focuses on the difference of the pronunciation of foreign accented speech compared to speech produced by native speakers. In second language learning and education practice, accentedness evaluation is very important to designing specific learning targets for different learners based on their level of accentedness, monitoring the learning progress and qualifying or quantifying the learning outcomes. One common experimental design in the study of perceived foreign accent is to have participants rate the degree of accentedness in various auditory stimuli, and then to relate these ratings to properties measured in the stimuli. Much research has been done to study the relationship between perceived foreign accent and acoustic characteristics of accented speech, such as voice onset time (VOT) \citep{major1987english}, word duration, stressed or unstressed vowel duration ratio \citep{shah2002temporal}, formants movement deviation from L1 acoustic values \citep{munro1993productions}, etc. In addition to the largely segmental acoustic properties suggested by the findings of previous studies, there are also some works focusing on supra-segmental information, including prosodic and global temporal properties, of foreign accented speech \citep{munro2010detection,kang2010relative}. Both those segmental and supra-segmental acoustic measurements have been shown to be correlated with perceived accentedness.

Though it is clear that the perception of accentedness is highly correlated with how far the phonological patterns of produced accented speech is from patterns of native speech, what has not been studied is whether the distance to the phonological patterns of the speaker's mother tongue matters. According to SLM, phonetic systems of L2 learners responds to L2 sounds by adding new phonetic categories, or modifying existing L1 phonetic categories \citep{flege1995second}. SLM claims that a new phonetic categories may be formed for an L2 sound given sufficient dissimilarity from the closest L1 sound and equivalence classification may block the category formation for an L2 sound, thus the original L1 phonetic category will be used to process both L1 and L3 sound, resulting in similar L2 production with L1 sound. Since SLM mainly focuses on the phonetic system, following studies also investigate the acquisition of L2 rhythm patterns \citep{rasier2007prosodic,ordin2015acquisition}. The findings in these studies reveal that while the general trend is becoming closer to the L2 rhythm patterns as the accent is milder, there still exist effects of L1 rhythm patterns for speakers from different L1 groups. Based those observation, we may ask

\begin{enumerate}
\item how the distance from the functional phonological system for accented speech to the actual L1 phonological system correlates with the perceived accentedness? Is the position of the phonological patterns of accented speech in the L1 and L2 phonological space a better choice to model the perception of accentedness?
\item Different L1s are at different relative positions with L2 in subspaces of the phonological system, mainly phonetic space and rhythmic space. For example, German and English are both stress-timed languages and thus are closer to each other on rhythmic space compared to French; Mandarin is syllable-timed language and has very different phonetic inventory compared to English so it is far from English on both subspaces. Will these contrastive properties be transferred to the accented speech during L2 acquisition? Furthermore, will those measurements on rhythmic space contribute more to the perception of accentedness compared to measurements on phonetic space for German speakers speaking English?
\end{enumerate}

The above are the research questions that will be investigated in this dissertation. Specifically, the current study will explore the relationship between measurements of phonological system with perceived accentedness by a computational model that extracts representative features of both phonetic and rhythmic subspaces. Given that the deviation of accented speech from the target L2 phonological patterns highly correlated with the accentedness score, this study investigates whether the deviation of accented speech from the original L1 phonological patterns has negative correlation with the accentedness score (i.e. the higher the deviation is, the milder the accent is); whether integrating measurements related to L1 can improve the modeling capability of accentedness perception; whether contrastive patterns of L1s and target L2 can be transferred to L1 accented speech.

\section{Significance of The Study}

There is a huge population of second (or higher order) language learners nowadays. The number of people living in a second language environment are also increasing with the economic globalization. Good understanding of the process of second language learning and accented speech perception is of great importance to successful speech communication in terms of both education, social science and communication science. The current study investigates the perception of accented speech. It aims to achieve better understanding of how the L1 of speakers with accent affects the perception of accentedness phonologically and how the phonetic system and rhythmic patterns contribute to the perception respectively. With a interdisciplinary research methods combining speech learning and perception theories with speech and language technologies, the current study will influence both the theoretic development of second language learning and accented speech perception and the technologies of Computer Assisted Pronunciation Training (CAPT) and Computer Aided Language Learning (CALL).

\section{Outline of The Dissertation}

The dissertation is divided into 8 chapters. Chapter 2 introduces the general background of the current study by reviewing several bodies of research on second language learning and accent speech perception theories and practices: including differential analysis of world languages, second language learning theories, acoustic characteristics of accented speech and computational model of accentedness perception. The motivation and predictions are then presented based on the literature review. Chapter 3 describes the methodology employed in this study including data collection, acoustic analysis and experimental design. Chapter 4 investigates the influence of L1's phonetic system on the accented speech perception. Chapter 5 investigates the influence of L1's rhythm patterns on the accented speech perception. Chapter 5 combines information of L1's phonetic and rhythmic patterns to build a computational model for better accentedness perception. Chapter 7 provides a general discussion of the experimental results and tries to extend the current theories on second langauge learning and accented speech perception. It also introduced the possible implications to both theoretic and practical studies on accented speech. Chapter 8 concludes the current study.



